---
title: "Exploratory data analysis"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(caret)
require(RANN)
```

## This is a note to self for exploratory data analysis.

I decided to use the orange dataset.

1- Loading the data:

```{r}
orange <- read.csv('https://raw.githubusercontent.com/selva86/datasets/master/orange_juice_withmissing.csv')

```


Let's have a look at the data:

```{r}
str(orange)
glimpse(orange)
head(orange)
summary(orange)
```

This is how like to check NAs, histograms, etc:

```{r}
orange%>%
  skimr::skim_to_wide() %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling()
```


Analysing categorical vars

```{r}
levels(orange$Purchase)
```

Categorical vars can be checked against each other

```{r}
table(orange$Purchase, orange$Store7)
```

According to skimr report the number of NAs is not propertional to size of the dataset. As a result, we can we can use knnImpute to fix the NAs

```{r}
preProcessMissingModel <- caret::preProcess(orange, method = 'knnImpute')

require(RANN)
orange <- predict(preProcessMissingModel, newdata = orange)
```

Checking whether we have any NAs
```{r}
anyNA(orange)
```

Let's look at the data again:

```{r}
orange%>%
  skimr::skim_to_wide() %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling()
```

Visually, we can detect some of the variables are skewed, but let's do it automatically. We are going to use moments library. 
```{r}
require(moments)

skewness.info <- orange %>% 
  select(-Purchase, -Store7) %>% #exclusing categorical vars
  skewness() %>% 
  data.frame()

skewness.info$Variables <- rownames(skewness.info)
colnames(skewness.info) <- c("Skewness", "Variable")

skewness.info %>% 
  ggplot(aes(x=Variable, y=Skewness))+
  geom_bar(stat = "identity", fill="darkgreen", alpha=.7)+
  coord_flip()

```

Positive skewness means it's skewed towards right.



A next step would be to transorm some variables. PctDiscMM is a good candidate, according to the skewness plot. Let's have a look at its density:

```{r}
orange %>% 
  ggplot(aes(x=PctDiscMM))+
  geom_density(fill="darkgreen", alpha=.4)
```

Same variable after log transform:
```{r}
orange %>% 
  ggplot(aes(x=log(PctDiscMM)))+
  geom_density(fill="darkgreen", alpha=.4)
```

And after square root transformation:

```{r}
orange %>% 
  ggplot(aes(x=sqrt(PctDiscMM)))+
  geom_density(fill="darkgreen", alpha=.4)
```


A next step would be to check for outliers. [will be added later..]



Analysis of variance. Let's assume there's a dependent variable and a few independent var. ANOVA is easy



```{r}
aov.ex <- aov(orange$PriceDiff~orange$PriceCH*orange$SpecialCH*orange$ListPriceDiff)
summary(aov.ex)

```

The stars next to the variables show the significant variables.



