---
title: "Exploratory data analysis"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(caret)
require(RANN)
```

## This is a note to self for exploratory data analysis.

I decided to use the orange dataset.

1- Loading the data:

```{r}
orange <- read.csv('https://raw.githubusercontent.com/selva86/datasets/master/orange_juice_withmissing.csv')

```


Let's have a look at the data:

```{r}
str(orange)
glimpse(orange)
head(orange)
summary(orange)
```

This is how like to check NAs, histograms, etc:

```{r}
orange%>%
  skimr::skim_to_wide() %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling()
```


Analysing categorical vars

```{r}
levels(orange$Purchase)
```

Categorical vars can be checked against each other

```{r}
table(orange$Purchase, orange$Store7)
```

According to skimr report the number of NAs is not propertional to size of the dataset. As a result, we can we can use knnImpute to fix the NAs

```{r}
preProcessMissingModel <- caret::preProcess(orange, method = 'knnImpute')

require(RANN)
orange <- predict(preProcessMissingModel, newdata = orange)
```

Checking whether we have any NAs
```{r}
anyNA(orange)
```

Let's look at the data again:

```{r}
orange%>%
  skimr::skim_to_wide() %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling()
```
